A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-01 02_Materials_and_Methods.Rmd
more data preparation steps

1. Downloading the Radon-B dataset with the R package c14bazAAR [@schmidC14bazAARDownloadPrepare2018], which allows to access several open radiocarbon archives. (11048)
2. Removing all dates without age information or age information outside of the limits of the Intcal13 calibration curve: 71 - 46401 BP [@reimer_intcal13_2013]. (10956)
3. Calibrating the ^14^C dates with the R package Bchron [@haslettSimpleMonotoneProcess2008], which implements the calibration algorithm with numerical integration.
4.

>>>>

1. Downloading the Radon-B dataset with the R package c14bazAAR [@schmidC14bazAARDownloadPrepare2018], which allows to access several open radiocarbon archives. (11048)
2. Removing all dates without age information or age information outside of the limits of the Intcal13 calibration curve: 71 - 46401 BP [@reimer_intcal13_2013]. (10956)
3. Calibrating the ^14^C dates with the R package Bchron [@haslettSimpleMonotoneProcess2008], which implements the calibration algorithm with numerical integration.
4. Reducing date selection to all dates whose $2\sigma$ calibrated age range overlap by at least one year with the predefined window of interest: 2200 -- 800 calBC. (7543)
5. Reducing the date selection to all dates taken from graves as indicated by the *Feature type* variable. (2361)
6. Transforming the variable *Feature type* via pattern matching to two new variables *burial type* (inhumation/cremation/unknown) and *burial construction* (mound/flat/unknown).
7. Manually defining a rectangular (EPSG:102013) research area with sufficient information in Central-, Northern and Northwesetern Europe based on perceived spatial date distribution (Figure XXX).
8. Reducing date selection to dates within the research area. (1894)
9.
